---
title: "buttRflyfish: reproduction of figure 2b from Nowicki et al. 2020"
author:
  - Gabriel A. Preising:
      email: gpreisin@stanford.edu
      institute: Stanford
      correspondence: true
  - Tatiana Bellagio:
      email: tbellg@stanford.edu
      instiftute: Stanford
      correspondence: false
  - Sebastian ToroArana:
      email: sebatoro@stanford.edu
      institute: Stanford
      correspondence: true
institute:
  - UofO: University of Stanford
  - UofA: Biology Department
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

<!-- With the following code you can access and display values from the yml header above. -->

Keywords: `r rmarkdown::metadata$keywords`

Highlights: `r rmarkdown::metadata$highlights`

<!-- The following code chunk defines some general settings how code chunks should behave. -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)

if (!file.exists("../data/raw_data/Nowicki_C_SPP_Males_data_ESM.csv")) {
  stop("Data not found: Go to analysis/data/raw_data and run getData.R")
}

```

<!-- The actual document text starts here: -->

# Introduction

This is a replication of figure 2A from [@nowicki2020]

# Background

# Methods

# Results

<!-- Here's some example analysis code: -->
```{r fig1, fig.cap="Reproduction of figure 2b from Nowicki et al. 2020.", echo = TRUE, results = 'hide', warning=FALSE, message = FALSE}
library(buttRflyfish)

data = load_data() # load data
model = run_model(data) # run MCMC model
p = otr_expression_plot(model,data) # plot differential expression results

```
Figure \@ref(fig:demo-plot) shows how we can have a caption and cross-reference for a plot

```{r demo-inline-code}
x <- round(pi, 2)
```

Here is an example of inline code `r x` in the middle of a sentence.

# Discussion

# Conclusion

# Acknowledgements

<!-- The following line inserts a page break  -->

\newpage

# References

<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->

::: {#refs}
:::

\newpage

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
